Structured Versus Decorated Cospans

### 2020-11-17 cospans.tex
setting straight something that was bothering me, hopefully now it's fine

On a highly related note, in what follows we are also interested in the existence of a left adjoint $L_F$ to an induced monoidal opfibration; the following result provides sufficient conditions for that.
%, which go hand-in-hand with \cref{cor:fcocMonGroth} and \cref{lem:fibrewiselimits}.

@@

Finally, if the original pseudofunctor is in fact lax monoidal $(F,\mu,\mu_0)$, the monoidal Grothendieck construction of \cref{lem:MonGroth} in the cocartesian case expresses $\bot_a$ as follows by \cref{eq:explicitstructure1}:
\begin{equation}\label{eq:initialinfibre}
\mathbf{1}\xrightarrow{\phi_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
\end{equation}
\end{rmk}

>>>>

Notice a subtlety in the above formulation: \cref{lem:MonGroth} provides a specifically induced monoidal structure on the fibres which becomes \cref{eq:explicitstructure1} in the cocartesian base case. If that fibrewise monoidal structure happens to itself be cocartesian, then it is necessarily isomorphic to \emph{any} other cocartesian structure on the fibres, by universal property of colimits. Therefore, we can simplify the above formulation to the one of the very \cref{thm:equiv} without having to specify that the structures came from monoidality of the pseudofunctor. DOES THIS MAKE SENSE TO ALL??

On a highly related note, in what follows we are also interested in the existence of a left adjoint $L_F$ to an induced monoidal opfibration; the following result provides sufficient conditions for that.

@@

Finally, if the original pseudofunctor is in fact lax monoidal $(F,\mu,\mu_0)$, the monoidal Grothendieck construction of \cref{lem:MonGroth} in the cocartesian case expresses $\bot_a$ as follows by \cref{eq:explicitstructure1}:
\begin{equation}\label{eq:initialinfibre}
\mathbf{1}\xrightarrow{\mu_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
\end{equation}
\end{rmk}
